---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rbm25

<!-- badges: start -->
<!-- badges: end -->

`{rbm25}` is a light wrapper around the rust [`bm25`](https://crates.io/crates/bm25) crate.
It provides a simple interface to the [Okapi BM25 algorithm](https://en.wikipedia.org/wiki/Okapi_BM25) for text search.

Note the package does not provide any text preprocessing, this needs to be done before using the package.


## Installation

You can install the development version of rbm25 like so:

``` r
# Development Version
# devtools::install_github("DavZim/rbm25")

# CRAN release
install.packages("rbm25")
```

## Example

The package exposes an R6 class `BM25` that can be used to query a text corpus.
For simplicity, there is also a `bm25_score()` function that wraps the `BM25` class.


```{r example}
library(rbm25)
# create a text corpus, where we want to find the closest matches for a query
corpus_original <- c(
  "The rabbit munched the orange carrot.",
  "The snake hugged the green lizard.",
  "The hedgehog impaled the orange orange.",
  "The squirrel buried the brown nut."
)

# text preprocessing: tolower, remove punctuation, remove stopwords
# note this is just an example and not the best way for larger amounts of text
stopwords <- c("the", "a", "an", "and")
corpus <- corpus_original |> 
  tolower() |> 
  gsub(pattern = "[[:punct:]]", replacement = "") |>
  gsub(pattern = paste0("\\b(", paste(stopwords, collapse = "|"), ") *\\b"),
       replacement = "") |> 
  trimws()

# define some metadata for the text corpus, e.g., the original text and the source
metadata <- data.frame(
  text_original = corpus_original,
  source = c("book1", "book2", "book3", "book4")
)
```


**Using the BM25 Class**

```{r bm25-class}
bm <- BM25$new(data = corpus, metadata = metadata)
bm

# note that query returns the values sorted by rank
bm$query(query = "orange", max_n = 2)
```

**Using the `bm25_score()` function**

```{r}
# note that bm25_score returns the score in the order of the input data
scores <- bm25_score(data = corpus, query = "orange")
data.frame(text = corpus, scores_orange = scores)
```
